Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-25 WSSSPE2_report/WSSSPE2_review.tex
Add a comma before 'and' for papers with more than two authors.

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Exploring Sustainability group are:
\begin{itemize}
\item Mario {Rosado de Souza} and Robert Haines and Caroline Jay. Defining
Sustainability through Developers' Eyes: Recommendations from an Interview
Study~\cite{wssspe2_rosada_de_souza}

\item Robert Downs, W. Christopher Lenhardt, Erin Robinson, Ethan Davis,
Nicholas Weber. Community Recommendations for Sustainable Scientific
Software~\cite{wssspe2_downs}

\item Abani Patra, Matthew Jones, Steven Gallo, Kyle Marcus and Tevfik Kosar.
Role of Online Platforms, Communications and Workflows in Developing Sustainable
Software for Science Communities~\cite{wssspe2_patra}

\item Marlon Pierce, Suresh Marru and Chris Mattmann.{WSSSPE2}: Patching It Up,
Pulling It Forward~\cite{wssspe2_pierce}

@@

\item Colin C. Venters, Michael K. Griffiths, Violeta Holmes, Rupert R. Ward and
David J. Cooke. The Nebuchadnezzar Effect: Dreaming of Sustainable Software
through Sustainable Software Architectures~\cite{wssspe2_venters}
\end{itemize}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Software Development Experiences Subgroup A are:

@@

\item Marcus Hanwell, Patrick O'Leary and Bob O'Bara. Sustainable Software
Ecosystems: Software Engineers, Domain Scientists, and Engineers Collaborating
for Science~\cite{wssspe2_hanwell}

\item W. Christopher Lenhardt, Stanley Ahalt, Matt Jones, J. Aukema, S. Hampton,
S. R. Hespanh, R. Idaszak and M. Schildhauer. {ISEES-WSSI} Lessons for
Sustainable Science Software from an Early Career Training Institute on Open
Science Synthesis~\cite{wssspe2_lenhardt}

@@

The papers that were discussed in the Software Development Experiences Subgroup
B are:

@@

\item Jordan Adams, Sai Nudurupati, Nicole Gasparini, Daniel Hobley, Eric
Hutton, Gregory Tucker and Erkan Istanbulluoglu. Landlab: Sustainable Software
Development in Practice ~\cite{wssspe2_adams}

@@

\item Carl Boettiger, Ted Hart, Scott Chamberlain and Karthik Ram. Building
software, building community: lessons from the {ROpenSci}
project~\cite{wssspe2_boettiger}

\item Yolanda Gil, Eunyoung Moon and James Howison. No Science Software is an
Island: Collaborative Software Development Needs in
Geosciences~\cite{wssspe2_gil}

\item Ted Habermann, Andrew Collette, Steve Vincena, Werner Benger, Jay Jay
Billings, Matt Gerring, Konrad Hinsen, Pierre de Buyl, Mark K\"{o}nnecke, Filipe
Rnc Maia and Suren Byna. The Hierarchical Data Format ({HDF}): A Foundation for
Sustainable Data and Software~\cite{wssspe2_habermann}

\item Eric Hutton, Mark Piper, Irina Overeem, Albert Kettner and James Syvitski.
Building Sustainable Software - The {CSDMS} Approach~\cite{wssspe2_hutton}

\item James S. Spencer, Nicholas S. Blunt, William A. Vigor, Fionn D. Malone, W.
M. C. Foulkes, James J. Shepherd and Alex J. W. Thom. The {H}ighly {A}ccurate
{N-DE}terminant ({HANDE}) quantum {Monte Carlo} project: Open-source stochastic
diagonalisation for quantum chemistry~\cite{wssspe2_spencer}
\end{itemize}

@@

\item Tom Crick, Benjamin A. Hall and Samin Ishtiaq. ``Can I Implement Your
Algorithm?'': A Model for Reproducible Research Software~\cite{wssspe2_crick}

\item Bryan Marker, Don Batory, Field G. Van Zee and Robert van de Geijn. Making
Scientific Computing Libraries Forward Compatible~\cite{wssspe2_marker}

@@

The papers that were discussed in the Code Testing \& Code Review group are:
\begin{itemize}
\item Thomas Clune, Michael Rilee and Damian Rouson. Testing as an Essential
Process for Developing and Maintaining Scientific Software~\cite{wssspe2_clune}

@@

\item Andrew E. Slaughter, Derek R. Gaston, John Peterson, Cody J. Permann,
David Andrs and Jason M. Miller. Continuous Integration for Concurrent {MOOSE}
Framework and Application Development on {GitHub}~\cite{wssspe2_slaughter}
\end{itemize}

>>>>

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Exploring Sustainability group are:
\begin{itemize}
\item Mario Rosado de Souza, Robert Haines, and Caroline Jay. Defining
Sustainability through Developers' Eyes: Recommendations from an Interview
Study~\cite{wssspe2_rosada_de_souza}

\item Robert Downs, W. Christopher Lenhardt, Erin Robinson, Ethan Davis, and
Nicholas Weber. Community Recommendations for Sustainable Scientific
Software~\cite{wssspe2_downs}

\item Abani Patra, Matthew Jones, Steven Gallo, Kyle Marcus, and Tevfik Kosar.
Role of Online Platforms, Communications and Workflows in Developing Sustainable
Software for Science Communities~\cite{wssspe2_patra}

\item Marlon Pierce, Suresh Marru, and Chris Mattmann. {WSSSPE2}: Patching It Up,
Pulling It Forward~\cite{wssspe2_pierce}

@@

\item Colin C. Venters, Michael K. Griffiths, Violeta Holmes, Rupert R. Ward, and
David J. Cooke. The Nebuchadnezzar Effect: Dreaming of Sustainable Software
through Sustainable Software Architectures~\cite{wssspe2_venters}
\end{itemize}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Software Development Experiences Subgroup~A are:

@@

\item Marcus Hanwell, Patrick O'Leary, and Bob O'Bara. Sustainable Software
Ecosystems: Software Engineers, Domain Scientists, and Engineers Collaborating
for Science~\cite{wssspe2_hanwell}

\item W. Christopher Lenhardt, Stanley Ahalt, Matt Jones, J. Aukema, S. Hampton,
S. R. Hespanh, R. Idaszak, and M. Schildhauer. {ISEES-WSSI} Lessons for
Sustainable Science Software from an Early Career Training Institute on Open
Science Synthesis~\cite{wssspe2_lenhardt}

@@

The papers that were discussed in the Software Development Experiences Subgroup~B are:

@@

\item Jordan Adams, Sai Nudurupati, Nicole Gasparini, Daniel Hobley, Eric
Hutton, Gregory Tucker, and Erkan Istanbulluoglu. Landlab: Sustainable Software
Development in Practice ~\cite{wssspe2_adams}

@@

\item Carl Boettiger, Ted Hart, Scott Chamberlain, and Karthik Ram. Building
software, building community: lessons from the {ROpenSci}
project~\cite{wssspe2_boettiger}

\item Yolanda Gil, Eunyoung Moon, and James Howison. No Science Software is an
Island: Collaborative Software Development Needs in
Geosciences~\cite{wssspe2_gil}

\item Ted Habermann, Andrew Collette, Steve Vincena, Werner Benger, Jay Jay
Billings, Matt Gerring, Konrad Hinsen, Pierre de Buyl, Mark K\"{o}nnecke, Filipe
Rnc Maia, and Suren Byna. The Hierarchical Data Format ({HDF}): A Foundation for
Sustainable Data and Software~\cite{wssspe2_habermann}

\item Eric Hutton, Mark Piper, Irina Overeem, Albert Kettner, and James Syvitski.
Building Sustainable Software - The {CSDMS} Approach~\cite{wssspe2_hutton}

\item James S. Spencer, Nicholas S. Blunt, William A. Vigor, Fionn D. Malone, W.
M. C. Foulkes, James J. Shepherd, and Alex J. W. Thom. The {H}ighly {A}ccurate
{N-DE}terminant ({HANDE}) quantum {Monte Carlo} project: Open-source stochastic
diagonalisation for quantum chemistry~\cite{wssspe2_spencer}
\end{itemize}

@@

\item Tom Crick, Benjamin A. Hall, and Samin Ishtiaq. ``Can I Implement Your
Algorithm?'': A Model for Reproducible Research Software~\cite{wssspe2_crick}

\item Bryan Marker, Don Batory, Field G. Van Zee, and Robert van de Geijn. Making
Scientific Computing Libraries Forward Compatible~\cite{wssspe2_marker}

@@

The papers that were discussed in the Code Testing \& Code Review group are:
\begin{itemize}
\item Thomas Clune, Michael Rilee, and Damian Rouson. Testing as an Essential
Process for Developing and Maintaining Scientific Software~\cite{wssspe2_clune}

@@

\item Andrew E. Slaughter, Derek R. Gaston, John Peterson, Cody J. Permann,
David Andrs, and Jason M. Miller. Continuous Integration for Concurrent {MOOSE}
Framework and Application Development on {GitHub}~\cite{wssspe2_slaughter}
\end{itemize}
